Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added slide to MSE training refinements, etc.

\begin{frame}
\frametitle{}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
	\begin{itemize_2pt}
		\item 5 major domains of practices
		\begin{enumerate_2pt}
			\item Book-keeping
			\item ?
			\item ?
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ Association with performance robust across industries and countries
	\item[] $\rightarrow$
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{itemize_2pt}
			\item 
			\item 
			\item 
			\item 
			\item 
		\end{itemize_2pt}
	\end{itemize_2pt}

@@

%\begin{frame}
%\begin{center}
%{ \Huge \textcolor{black}{Classical MSME Training}}
%\end{center}
%\end{frame}

@@

\begin{frame}
\frametitle{Evidence of Impact}
	\begin{itemize_2pt}
	\item First wave (Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citet{Gine2014} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Evidence of Impact}
	\begin{itemize_2pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}[label=McK2020_profits]
\frametitle{Evidence of Impact}

@@

\begin{frame}
\frametitle{Targeting Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeting Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as entrepreneurship programs in school and university
		\item Example: University final year course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item
			\item
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeting Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item
	\item
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

>>>>

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
	\begin{itemize_2pt}
		\item 5 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item ?
			\item ?
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ Association with performance robust across industries and countries
	\item[] $\rightarrow$
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g., 
		\end{enumerate_2pt}
	\end{itemize_2pt}

@@

@@

\begin{frame}
\frametitle{Impact on Performance}
	\begin{itemize_2pt}
	\item First wave (Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citet{Gine2014} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Performance}
	\begin{itemize_2pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}[label=McK2020_profits]
\frametitle{Impact on Performance}

@@

\begin{frame}
\frametitle{Targeted Training}
	Refinements of the classical model

	\begin{itemize_2pt}
		\item Targeting \textcolor{bdf}{specific subgroups} of the population
		\begin{itemize_2pt}
			\item Treating individuals with particular promise (e.g., high-growth firms)
			\item[] $\rightarrow$ \textcolor{bdf}{Maximizing impact} (or cost-effectiveness)
			\item Serving marginalized or disadvantaged groups
			\item[] $\rightarrow$ Alleviating \textcolor{bdf}{particularly severe constraints}
			\item[] $\rightarrow$ 
			\item \textcolor{bdf}{Maximizing statistical power} through homogeneity
		\end{itemize_2pt}

		\item Training of skills in \textcolor{bdf}{particular domains}
		\begin{itemize_2pt}
			\item Alleviating \textcolor{bdf}{specific constraints}
			\item Investigating mechanisms of treatment impact
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as entrepreneurship programs in school and university
		\item Example: University final year course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item
			\item
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item
	\item
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}
